DOpElib:\\ Differential Equations and Optimization Environment

### 2016-04-05 Examples/PDE/StatPDE/Example10/content.tex
Added Trilinos Direct Solvers and demonstrate them in example PDE/StatPDE/Example10

>>>>

Finally this example demonstrates how to use the direct solvers provided by trilinos. 
This is done by the line 
\begin{verbatim}
typedef TrilinosDirectLinearSolverWithMatrix
         <SPARSITYPATTERN, MATRIX, VECTOR> LINEARSOLVER;
\end{verbatim}
interfacing to the trilinos library. The selection of the precise direct solver can 
be done using the parameter file.
